|

### 2023-03-21 paper_comparison/paper_comparison/paper_comparison.Rmd
update bib

@@

# Acknowledgement

This research is enabled by the use of the following `R` packages:
cli, curl, dplyr, ggplot2, jsonlite, lmtest, mpoly, progress, tibble, ggmosaic, purrr, tidyr, readr, stringr, here, kableExtra, patchwork, rcartocolor. The study website is powered by pythonAnywhere and the Flask web framework. The jsPsych framework is used to create behavioral experiments that run in our study website.

The article was created with rticles (ref here), knitr (ref here) and R Markdown (ref here). The project's Github repository (link here) contains all materials required to reproduce this article.

@@

\newpage

>>>>

(put citation https://www.tandfonline.com/doi/full/10.1080/26939169.2021.1920866)

@@

# Acknowledgements

These `R` packages are used for the work: 
`cli` [@cli], `curl` [@curl], `dplyr` [@dplyr], `ggplot2` [@ggplot2], `jsonlite` [@jsonlite], `lmtest` [@lmtest], `mpoly` [@mpoly], `progress` [@progress], `tibble` [@tibble], `ggmosaic` [@ggmosaic], `purrr` [@purrr], `tidyr` [@tidyr], `readr` [@readr], `stringr` [@stringr], `here` [@here], `kableExtra` [@kableextra], `patchwork` [@patchwork], `rcartocolor` [@rcartocolor]. The study website is powered by `PythonAnywhere` [@pythonanywhere] and the `Flask` web framework [@flask]. The `jsPsych` framework [@jspsych] is used to create behavioral experiments that run in our study website.

The article was created with R packages `rticles` [@rticles], `knitr` [@knitr] and `rmarkdown` [@rmarkdown]. The project's Github repository (link here) contains all materials required to reproduce this article.

@@

<!-- \newpage -->
